ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-01 paper.tex
Cleared commented code

\author{J.C. Lock\inst{1} \and
  G. Cielniak\inst{1} \and
  A.G. Tramontano\inst{2} \and
  N. Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universit\`{a} degli studi di Padova, Italy
}

@@

%Mobile devices that can detect objects and guide PwVI in real-time using on-board processing power has become more feasible in recent years thanks to improvements in mobile computing and image processing methods.
Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture. 
%that requires the user to send a photo of their environment to a Mechanical Turk worker who sends the position of the requested object within the picture back to the user. 
%The SIFT based system in~\cite{schauerte2012assistive} is an example of a markerless system.

@@

Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy trade-off, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models. 
%MobileNet~\cite{howard2017mobilenet} in particular is a 2-stage network designed specifically for mobile platforms with moderate precision levels, but can reach around 10 frames per second on a mobile platform.
%The two-stage models, such as Faster R-CNN~\cite{ren2015faster}, use a region proposal network approach where an external algorithm proposes a region of interest that the classifier uses as input to recognise any objects. 
%They typically reach higher accuracy, but at the cost of increased memory and computational resource requirements~\cite{liu2018deeplf}.
%On the other hand, single-stage methods apply multiple differently sized windows over the image and checks if any objects appear in those windows. 
%These methods, such as Single-Shot Detection (SSD)~\cite{liu2016ssd} and You Only Look Once (YOLO)~\cite{redmon2018yolo}, typically need less computational resources, but at the cost of decreased accuracy.
%Marrying a single-stage method to a feature extractor yields higher accuracy, by at the cost of increased computational resources. 
%There is therefore a fine speed-accuracy trade-off to be made, particularly in a mobile context where processing resources are limited. 
%MobileNet~\cite{howard2017mobilenet} is a classifier network that can be used as a feature extractor  that introduced depth-wise separable convolutions that decrease the number of operations needed to make a convolution.
%This leads to model that uses much less memory, but again with a small drop in accuracy.

@@

%The ActiVis project's goal is developing a mobile system that can guide a PwVI towards their desired destination with minimal user input or intervention. 
%This work focuses on guiding a user towards an object in one static environment and is limited to 2 dimensions (pan and tilt).

@@

%The error, $e$, is defined as the difference between the desired object and the object currently within view. 
Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.

In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
The design and implementation of this controller are discussed next.

%\section{Human Controller}\label{sec:human-controller}

%The POMDP controller that we implemented for this work is an extension to the MDP-based controller we made for the experiments described in~\cite{lock2019active}.
%It works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
%The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
%A new waypoint is generated when the user finds the current waypoint or finds another ancillary object.

@@

A POMDP model is represented by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate. 
%$\mathbf{b}$ is updated for every timestep and action-observation pair.
The POMDP's parameters and training process are discussed next. 
%This update is done with

%\begin{equation}
  %b_t(s') = \eta\Omega(o, s', a)\sum_{s\in\mathbf{S}}\mathbf{T}(s, a, s')b_{t-1}(s), 
%\end{equation}
%where $\eta$ is a normalisation factor.

%The state space, reward function and transition matrix are conceptually similar the same as the MDP described in~\cite{lock2019active}. 
%The major difference is the addition of an observation matrix that defines the probability of being in any given state after making a new observation.
%In essence, it is a measure of the sensor accuracy, and in this case it describes the object detector's classification accuracy and recall.
%These parameters are given by the following.

@@

%\begin{equation*}
  %t(s, a, s') = t(\textrm{keyboard}, \textrm{UP}, \textrm{monitor}) = 0.16.
%\end{equation*}
%An image displaying this relationship can be seen in Fig.~\ref{fig:openimage}.

@@

%Non-visual feedback allows the app to be used by PwVI.
%This was done by combining an audio interface that provides non-visual guidance instructions, the POMDP controller and object detector onto a mobile app.
%Each of these aspects and their implementation are discussed here.

%\subsubsection{Audio Interface}

We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
% that can be used by a PwVI by adding .% onto a mobile phone that can generate and provide guidance instructions for a user.  
%ActiVis's target audience are PwVI and therefore provides guidance instructions in a non-visual manner that is intuitive and easy to understand. 
To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly. 
A similar approach was used in~\cite{schauerte2012assistive}.
%This interface enables ActiVis to describe the location of a waypoint to a user in the pan and tilt dimensions.

%\subsubsection{Object Detector}

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mean average precision (mAP) of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
The full SSD model achieves a slightly higher mAP (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).
%Tiny-DSOD~\cite{li2018tinydsod}, an alternative to SSD-Lite, has similar precision and computing requirements (mAPs=0.23, parameters=1.15M, FLOPS=1.12B), but we found that SSD-Lite produced better results for this application and chose to implement it in ActiVis.

The network was trained with a maximum of 10000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.
%We also built our own test small dataset to test the model with.\todo{should we include this? Doesnt look very good}
%This dataset contains 459 images for each of the objects in $\mathbf{U}$ in different sizes and orientations and the objects used were the same objects that were used in the experiments. 
%\todo{add mAPs we achived}

%\subsubsection{Action Generator}

To generate new waypoints, the system uses the policy file output from the POMDP model's training process that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
%Each grid square represents a \SI{35}{\degree} angular translation and the grid encompasses a \SI{210}{\degree}$\times$\SI{210}{\degree} field of view. 
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.

@@

To evaluate the guidance system's effectiveness, we designed a set of experiments to measure its performance in driving a user towards a target object within a static environment. 
We conducted an additional set of experiments with an alternative system that relies on a user's intuition and prior knowledge to generate actions instead, to act as a baseline measurement for our system's results. 
%This alternative system does not provide any guidance instructions to the user.
%Instead, it provides the user with raw observations from the object classifier and relies on the user's intuition and prior knowledge to generate actions. 
%The goal of both the guided and unguided experiment cases were to find an object within a static environment.

Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects. 
%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences which is not a problem since most offices contain the same basic furniture and objects. 
The objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects between experiments. 
The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
%This process is modelled by the schematic in Fig.~\ref{fig:sys-diagram-no-controller} where the human acts as both the actuator and controller.
In this case, the human acts as both the controller and actuator. 
The app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

%\begin{figure}
  %\centering
  %\includegraphics[width=0.4\textwidth]{figures/control_loop_no_controller.png}
  %\caption{The control loop with the human acting as both manipulator and controller. }\label{fig:sys-diagram-no-controller}
%\end{figure}

%Each participant was verbally informed prior to each experiment what the target object was.
%The learning effect was ignored in order to mimic the normal search behaviour described earlier and allow full use of prior knowledge. 
%This process performed once for each object in the experiment set.

@@

The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
This also isolated the performance measurement to the guidance system alone.
An experiment run started with the experiment staff selecting the target.
%and was terminated when the target object was found or the 45 second time limit was reached.
%This process performed once for each object in the experiment set.

%\subsection{Environment Setup}

%The environment and the object placement within it for both experiments was modelled on a typical office.
%Measures were taken to ensure that both office environments were unique in layout and object placement. 
%However, for the larger, more static objects (e.g.\ a desk or door) there is cross-experiment occurrences, which is not a problem since most offices contain the same basic furniture and objects. 
%These objects were placed in different locations relative to each other for the 2 experiments to minimise any learning effects that may occur between the experiments. 
%The objects in the guided experiment environment are

%\begin{equation*}
  %\mathbf{u}_{guided} = \{ door, desk, chair, whiteboard, mouse, laptop, backpack, mug \},
%\end{equation*}
%while the objects in the unguided experiment are

%\begin{equation*}
  %\mathbf{u}_{unguided} = \{ door, desk, chair, whiteboard, mouse, monitor, telephone, keyboard \}.
%\end{equation*}
%A picture of the unguided experiment environment is given in Fig.~\ref{fig:experiment-env}.

%\begin{figure}
  %\centering
  %\includegraphics[width=0.7\textwidth]{figures/environment.png}
  %\caption{A picture of the experiment setup. }\label{fig:experiment-env}
%\end{figure}

@@

%We set an upper time limit for each object search run of 45 seconds.
%When this upper threshold was reached, the search was recorded as a failure and the next run was started.

@@

%\todo{Should I add CDF?}
The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.%, while Fig.~\ref{fig:cum-time} shows the cumulative distribution functions (CDF) for the search times as a function of the total number of objects found.

@@

%\begin{figure}
  %\centering
  %\includegraphics[width=0.7\textwidth]{figures/cumplot_time_to_target.png}
  %\caption{A set of CDFs comparing the time to target. }\label{fig:cum-time}
%\end{figure}

%To compensate for the different numbers of targets found per participant and for each experiment setup, we average each participant's results, giving us 10 samples per experiment. 
From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.
%These results are summarised in Table~\ref{tab:results}. 
%With this 27\% reduction in total time spent searching for a target object, we can conclude that a user benefits from using our smart guidance system as opposed to relying on a simple object reader. 
%This is supported by the CDFs in Fig.~\ref{fig:cum-time} that show that \todo{Discuss the less number of objects found and how it is not statistically signioficatn. Perhaps show it in CDF}

@@

To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.%, enhancing user experience and improving ease of use.
%\todo{maybe cite paper that says less exertion is good}.

@@

%\begin{figure}
  %\centering
  %\includegraphics[width=0.7\textwidth]{figures/boxplot_angle.png}
  %\caption{A set of boxplots comparing the angular distance the device travelled for each experiment. }\label{fig:boxplot-angle}
%\end{figure}

%\begin{figure}
  %\centering
  %\includegraphics[width=0.7\textwidth]{figures/boxplot_dist.png}
  %\caption{A set of boxplots comparing the distance the device travelled for each experiment. }\label{fig:boxplot-dist}
%\end{figure}

>>>>

\author{J.C. Lock\inst{1} \and
  A.G. Tramontano\inst{2} \and
  S. Ghidoni\inst{2} \and
  N. Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universit\`{a} degli studi di Padova, Italy
}

@@

Early attempts to solve this guidance problem used markers encoded with object or environmental information and a smartphone that scans the environment for these simple patterns~\cite{gude2013blind,manduchi2012mobile}. 
The device uses audio feedback to read out the embedded information or guide the user towards the markers. 
Improvements to feature detectors have made it viable~\cite{redmon2016you} to replace markers with real objects, while an alternative guidance approach is proposed in~\cite{bigham2010vizwiz} which uses a Mechanical Turk worker to manually locate and give guidance instructions to the desired object within a user-provided picture.

@@

Object detectors mainly come in 2 flavours: 2-stage models that use an external algorithm to select regions of interest to perform object inference on~\cite{ren2015faster}, and single-stage models that generate multiple, differently-sized windows and checks each window for any objects.
Between the 2 types, there is a speed-accuracy trade-off, where 2-stage models typically produce more accurate results, but are slower and require more computing resources~\cite{liu2018deeplf}.
On the other hand, single-stage models, such as SSD and MobileNet~\cite{liu2016ssd,howard2017mobilenet} produce less accurate results, but with drastically less parameters and FLOPS required to perform object inference than the 2-stage models.

@@

@@

Adding a human into the loop adds an additional block, \emph{H}, representing a human that receives a control signal, \emph{u}, from the controller, \emph{K}. 
However, the challenge is that a person may interpret \emph{u} in any unpredictable way that results in the signal \emph{u*} that points the camera, \emph{P}, to a new location containing a new object observation, \emph{y}.
It is therefore important to design \emph{K} to be robust enough to accommodate different user habits and limitations and ensure that \emph{u*} tracks \emph{u} as closely as possible. 
The object detector's classification errors, \emph{n}, is added to the feedback loop as a noise signal and affects \emph{K}'s output.

In our previous work~\cite{lock2019active}, we assumed a perfect classifier and solved the problem using a Markov decision process (MDP). 
In this work we do away with that somewhat naive assumption and extend the MDP and implement a POMDP-based controller that can handle classification uncertainties in object detectors and classifiers. 
This controller works by generating a trail of virtual waypoints for the user to point the camera towards that eventually leads to the target object.
The waypoint positions are based on the model's pre-trained internal knowledge of the inter-object spatial relationships and they are placed in a way that maximises the probability of the user finding the target object.
The design and implementation of this controller are discussed next.

@@

A POMDP model is represented by the 8-tuple $(\mathbf{S}, \mathbf{A}, \mathbf{T}, \mathbf{R}, \mathbf{\Omega}, \mathbf{O}, \mathbf{b}, \gamma)$, where $\mathbf{S}$ represents a finite set of discrete states, $\mathbf{A}$ is a set of discrete actions, $\mathbf{T}$ is a matrix containing the probabilities of transitioning from state $s$ to state $s'$, $s, s' \in \mathbf{S}$, after executing action $a$, $a \in \mathbf{A}$, and $\mathbf{R}$ is the reward the agent receives executing action $a$ and reaching state $s'$.
$\mathbf{\Omega}$ is the set of possible state observations, while the matrix $\mathbf{O}$ contains the probabilities of making state observation $\omega$, $\omega \in \mathbf{\Omega}$, when in state $s$ after executing action $a$.
Finally, $\mathbf{b}$ is the belief vector containing the state probability distribution and $\gamma$ is a discount factor that prioritises long-term over short-term rewards and affects the model's convergence rate. 
The POMDP's parameters and training process are discussed next.

@@

@@

We implemented the object detector and POMDP controller into an Android app and combined it with an audio interface that provides non-visual guidance instructions.
To avoid blocking a user's access to ambient sounds, we use non-intrusive bone-conducting headphones to transmit the audio signals to the user.

To describe the waypoints' pan and tilt positions, we implemented an improved version of the interface described in~\cite{bellotto2013} that uses a spatialised audio signal.
However, since our headphones bypass the ear's pinnae that allow a person to localise the height~\cite{roffler1968factors}, we spatialise the audio in the pan dimension only.
To convey the tilt angle, we instead exploit a human's natural association of high and low sound sources with a high and low sound frequency respectively~\cite{blauert1997spatial} and adjust the sound source's pitch accordingly. 
A similar approach was used in~\cite{schauerte2012assistive}.

SSD-Lite is a single-stage object detection and classification network that is based on the SSD architecture that implements MobileNetV2~\cite{sandler2018mobilenetv2}.
This is a lightweight model that requires relatively little memory to perform inference tasks, making it suitable for mobile platforms. 
This model achieves a mean average precision (mAP) of 0.22 with 4.3M parameters and 0.8B FLOPS~\cite{li2018tinydsod} on the COCO dataset.
The full SSD model achieves a slightly higher mAP (0.25), but with significantly more parameters (34.3M) and FLOPS (34.36B).

The network was trained with a maximum of 10000 object samples for each class in $\mathbf{U}$, taken from the OpenImages dataset~\cite{openimages}, with a 60\%/20\%/20\% split for training, validation and testing respectively.
We set a relatively high confidence threshold of 0.7 to reduce the likelihood of false-positives.
With 120 training epochs with 1000 iterations each, we achieved a mAP of 0.16 on this dataset and produced a TensorFlow Lite model that is compatible with Android and we used this model to implement an SSD-Lite object detector onto a mobile device.

To generate new waypoints, the system uses the policy file output from the POMDP model's training process that defines the best location to place the next search waypoint based on the device's current state.
This state is tracked by the device throughout the app's runtime by performing object detection and recording the device's previous search locations and previous waypoint positions
The latter is done by disretising the world into a $6\times6$ grid, each representing a \SI{35}{\degree} rotation, and setting the relevant grid unit's $v$ value.
This setup gives the state access to perfectly observable $n$ and $v$ parameters, while $o$ is generated by the object detector. 
When the device makes a new state observation, $\omega$, either because the user rotates the device past \SI{35}{\degree} or sees a new object, the device triggers the controller to generate a new waypoint location.
The controller uses $\omega$ to update $\mathbf{b}$ and queries the policy for the best location to place the new waypoint. 
The policy output is an action from $\mathbf{A}$ that indicates the next adjacent grid square to place the waypoint, e.g.\ `UP' output would result in a waypoint being placed one grid square above the grid square within view.

@@

To evaluate the guidance system's effectiveness, we designed a set of experiments to measure its performance in driving a user towards a target object within a static environment. 
We conducted an additional set of experiments with an alternative system that relies on a user's intuition and prior knowledge to generate actions instead, to act as a baseline measurement for our system's results.

Both experiment environments and the object placements within them were modelled on a typical office and care was taken to ensure that both environments were unique in layout and object placement, though some cross-experiment occurrences appear with the larger, more static objects. 
To minimise any cross-experiment learning effects, 2 different sets of objects were used for each experiment and any objects that occurred in both experiments were placed at different positions for each experiment. 
The objects in the guided experiment environment are $\mathbf{u}_{guided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $laptop$, $backpack$, $mug \}$, while the objects in the unguided experiment are $\mathbf{u}_{unguided} = \{ door$, $desk$, $chair$, $whiteboard$, $mouse$, $monitor$, $telephone$, $keyboard \}$.

@@

For this experiment, the mobile camera and object detector acts as the participants' eyes and informs them about the objects within the camera's view.
It is then up to the participant to exploit their prior knowledge and intuition to manipulate the camera and find the target object. 
In this case, the human acts as both the controller and actuator. 
The app only reads out the objects upon the user's request by tapping on the screen. 
When the target object comes within the camera's view and is correctly detected, the device vibrates to inform the participant.

@@

The participants were not told what the targets objects were in this experiment to eliminate the possibility of them ignoring the guidance instructions in order to try and find the target object faster themselves.
This also isolated the performance measurement to the guidance system alone.
An experiment run started with the experiment staff selecting the target.

@@

@@

The time it takes to find a target object is an important indicator of system performance, where less time indicates a shorter search time and increased performance.
The data for the search times for each experiment are shown in Fig.~\ref{fig:boxplot-time}.

@@

From Fig.~\ref{fig:boxplot-time}, it can be seen that the guidance system reduced the overall time it took the participants to find each target object.
This is confirmed by the data that show an average search time of 12.5s for the guided experiment and 17.2s for the unguided case ($p_{kw}=0.045$), an improvement of around 27\%.

@@

To give an indication of the effort required to find each target, we look at the mobile device's displacement data. 
In this case, less device displacement is desirable, since it implies less physical exertion was demanded from the user.

@@
